Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
compromise wording

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
using reduced-order quadrature\cite{Canizares:2014fya,Smith:2016qas}, leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Veitch:2014wba,Ashton:2021anp,Islam:2022afg,Roulet:2022kot,Lee:2022jpn,Lange:2018pyp,Wofford:2022ykb}.
While these avenues are promising for standard GW problems, they rely on
assumptions that may not hold for analyses targeting additional physical effects
beyond standard CBCs in GR, such as lensing and deviations from GR, or may use
approximations that do not compute the Bayesian likelihood exactly.

@@

In this work, we present a lightweight, flexible, and high performance
framework to infer GW event parameters in a fully-Bayesian analysis. Our
framework implements the following techniques to achieve its performance:
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item likelihood heterodyning,
\item differentiable waveform models,
\item a normalizing-flow enhanced Markov chain Monte-Carlo (MCMC) sampler, and
\item native support for hardware accelerators.
\end{enumerate}
All these components, working jointly, come together into a high-performance
and high-fidelity PE pipeline, which can achieve ${\gtrsim}10^3\times$ speed
ups relative to traditional tools without sacrificing accuracy for efficiency
or making limiting assumptions about the target parameter space.

>>>>

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
using reduced-order quadrature\cite{Canizares:2014fya,Smith:2016qas}, leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Veitch:2014wba,Ashton:2021anp,Islam:2022afg,Roulet:2022kot,Lee:2022jpn,Lange:2018pyp,Wofford:2022ykb}.
While these avenues are promising for standard GW problems, they rely on
assumptions that may not hold for analyses targeting additional physical effects
beyond standard CBCs in GR, such as lensing and deviations from GR.

@@

In this work, we present a lightweight, flexible, and high performance
framework to infer GW event parameters in a fully-Bayesian analysis. Our
framework implements the following techniques to achieve its performance:
\begin{enumerate}
\setlength{\itemsep}{0pt}
\item likelihood heterodyning,
\item differentiable waveform models,
\item a normalizing-flow enhanced Markov chain Monte-Carlo (MCMC) sampler, and
\item native support for hardware accelerators.
\end{enumerate}
All these components, working jointly, come together into a high-performance
and high-fidelity PE pipeline, which can achieve ${\gtrsim}10^3\times$ speed
ups relative to traditional tools without compromising generality for efficiency
or making limiting assumptions about the target parameter space.
